Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
self contained html

---
title: "Formulating Regional Typologies"
author: "CIFOR-ICRAF Indonesia"
date: last-modified
date-format: "dddd MMM D, YYYY"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
reference-location: document
editor: visual
---

>>>>

---
title: "Formulating Regional Typologies"
author: "CIFOR-ICRAF Indonesia"
date: last-modified
date-format: "dddd MMM D, YYYY"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
    self-contained: true
reference-location: document
editor: visual
---
